Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-11-29 paper/main.tex
split figure; extend caption

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.49\textwidth]
        {docs/source/_static/performance/computation-time-with-initial-agents.pdf}
    \includegraphics[width=0.49\textwidth]{docs/source/_static/performance/flamegraph.pdf}
    \caption{TODO}
    \label{fig:performance}
\end{figure}

\begin{figure}[H]
    \centering
    \includegraphics[width=0.5\textwidth]{figures/crm_divide/timings.pdf}%
    \includegraphics[width=0.5\textwidth]{figures/crm_divide/time-evolution.pdf}%
    \caption{TODO}
    \label{fig:timings-crm_divide}
\end{figure}

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.5\textwidth]{figures/crm_divide/time-evolution.pdf}%
    \caption{TODO}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \begin{tikzonimage}[width=0.5\textwidth]
        {docs/source/_static/performance/computation-time-with-initial-agents.pdf}
        \node at (0, 1)[anchor=north west]{\textbf{A}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.5\textwidth]
        {figures/crm_divide/timings.pdf}
        \node at (0, 1)[anchor=north west]{\textbf{B}};
    \end{tikzonimage}\\
    \begin{tikzonimage}[width=\textwidth]
        {docs/source/_static/performance/flamegraph.pdf}
        \node at (0.02, 0.98)[anchor=north west]{\textbf{C}};
    \end{tikzonimage}\\
    \caption{
        (A) Wall time of the performed simulation with increasing number of final agents inside the
        simulation domain.
        (B) Distribution of computation time for the division script utilized in
        section~\ref{sec:application-1-with-division}.
        (C) Flamegraph of a typical simulation showcasing frequency of function calls for
        parallelized execution of simulations.
    }
    \label{fig:timings-crm_divide}
\end{figure}
